Make any stupid plot you want

### 2021-02-26 draft/sections/math.tex
more figures

\begin{figure}[H]
    \includegraphics[width=.5\textwidth]{figures/math/k_different_types.png}
    \caption{The topological base space \dbase\ encodes the connectivity of the data space, for example if the data is independent points or a map or on a sphere}
    \label{fig:base_space_types}
\end{figure}
As illustrated in figure~\ref{fig:base_space_types}, \dbase\ is akin to an indexing space into \dtotal\ that describes the structure of \dtotal.  \dbase\ can have any number of dimensions and can be continuous or discrete.

\begin{figure}[H]
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    \caption{The base space \dtotal\ is divided into fiber segments \dfiber. The base space \dbase\ acts as an index into the records in the fibers.
    \note{this figure might be good all the way up top to lay out the components of fb}}
    \label{fig:base_space_div}
\end{figure}

Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}. In figure~\ref{fig:base_space_div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. 
As with fibers and monoids, we can decompose the total space into components $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
which is a decomposition of \dfiber. The \dbase\ remains the same because the connectivity of records does not change just because there are fewer elements in each record.
\begin{figure}[ht!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2k.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_line} the total space \dtotal\ is discrete over points $\dbasepoint \in \dbase$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_plane} \dtotal\ lies over the continuous interval \dbase, meaning the records in the fiber are sampled from a continuous space. 
    \note{revamp figure: F=Plane, k1 = dots, k2=line}}
    \label{fig:base_example}
\end{figure}

@@

As a first pass for implementation purposes, we identify a minimal \vfiber\ associated with each $\vartist^{\prime}$ that defines what visual characteristics of the graphic must originate in the data such that the graphic is identifiable as a given chart type.
\begin{figure}[H]
    \caption{Each of these graphics is generated by a different artist \vartist which is the equivalance class of scatter plots $\vartist^{\prime}$\note{this is gonna be a whole bunch of scatter plots}}
    \label{fig:artist_equivalence}
\end{figure}

For example, a scatter plot of red circles is the output of one artist, a scatter plot of green squares the output of another, as shown in figure~\ref{fig:artist_equivalence}. These two artists are equivalent since their only difference is in the literal visual encodings (color, shape). Shape and color could also be defined in \vmark\, but the position must come from the fiber $\vfiber=(xpos,ypos)$ since fundementally a scatter plot is the plotting of one position against another\cite{friendlyBriefHistoryData2008}. We also use this criteria to identify derivative types, for example the bubble chart\cite{tufteVisualDisplayQuantitative2001} is a type of scatter where by definition the glyph size is mapped from the data. The criteria for equivalence class membership serves as the basis for evaluating invariance\cite{kindlmann2014algebraic}. 
\end{document}

>>>>

\begin{figure}[H]
    \includegraphics[width=.5\textwidth]{figures/math/k_different_types.png}
    \caption{The topological base space \dbase\ encodes the connectivity of the data space, for example if the data is independent points or on a plane or a sphere}
    \label{fig:base_space_types}
\end{figure}
As illustrated in figure~\ref{fig:base_space_types}, \dbase\ is akin to an indexing space into \dtotal\ that describes the structure of \dtotal.  \dbase\ can have any number of dimensions and can be continuous or discrete.

\begin{figure}[H]
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    \caption{The base space \dtotal\ is divided into fiber segments \dfiber. The base space \dbase\ acts as an index into the records in the fibers.}
    \label{fig:base_space_div}
\end{figure}

Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}. In figure~\ref{fig:base_space_div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. 
As with fibers and monoids, we can decompose the total space into components $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
which is a decomposition of \dfiber. The \dbase\ remains the same because the connectivity of records does not change just because there are fewer elements in each record.
\begin{figure}[ht!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_line} the total space \dtotal\ is discrete over points $\dbasepoint \in \dbase$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_plane} \dtotal\ lies over the continuous interval \dbase, meaning the records in the fiber are sampled from a continuous space.} 
    \label{fig:base_example}
\end{figure}

@@

As a first pass for implementation purposes, we identify a minimal \vfiber\ associated with each $\vartist^{\prime}$ that defines what visual characteristics of the graphic must originate in the data such that the graphic is identifiable as a given chart type.
%%
%%\begin{figure}[H]
%%   \caption{Each of these graphics is generated by a different artist \vartist which is the equivalance class of scatter plots $\vartist^{\prime}$\note{this is gonna be a whole bunch of scatter plots}}
%%    \label{fig:artist_equivalence}
%%\end{figure}

For example, a scatter plot of red circles is the output of one artist, a scatter plot of green squares the output of another. These two artists are equivalent since their only difference is in the literal visual encodings (color, shape). Shape and color could also be defined in \vmark\, but the position must come from the fiber $\vfiber=(xpos,ypos)$ since fundementally a scatter plot is the plotting of one position against another\cite{friendlyBriefHistoryData2008}. We also use this criteria to identify derivative types, for example the bubble chart\cite{tufteVisualDisplayQuantitative2001} is a type of scatter where by definition the glyph size is mapped from the data. The criteria for equivalence class membership serves as the basis for evaluating invariance\cite{kindlmann2014algebraic}. 
\end{document}
